SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-07-26 scipy-1.0/consortium.tex
Correct author list

Christian Brueffer$^{39}$, 
Christian H\"aggstr\"om$^{40}$, 
Clark Fitzgerald$^{41}$, 
David A. Nicholson$^{42}$, 
David R Hagen$^{43}$, 
Dmitrii V. Pasechnik$^{44}$, 
Emanuele Olivetti$^{45}$, 

@@

Eric Wieser$^{46}$, 
Fabrice Silva$^{47}$, 
Felix Lenders$^{48,49,50}$, 
Florian Wilhelm$^{51}$, 

@@

Gavin A. Price$^{52}$, 
Gert-Ludwig Ingold$^{53}$, 
Gregory E. Allen$^{54}$, 
Gregory R. Lee$^{55,56}$, 
Herv\'e Audren$^{57}$, 
Irvin Probst$^{58}$, 
J\"org P. Dietrich$^{59,60}$, 
Jacob Silterra$^{61}$, 
James T Webber$^{62}$, 
Janko Slavi\v{c}$^{63}$, 
Joel Nothman$^{64}$, 
Johannes Buchner$^{65,66}$, 
Johannes Kulick$^{67}$, 

@@

Jos\'e Vin\'icius de Miranda Cardoso$^{68}$, 
Joscha Reimer$^{69}$, 
Joseph Harrington$^{70}$, 
Juan Luis Cano Rodr\'iguez$^{71}$, 
Juan Nunez-Iglesias$^{72}$, 
Justin Kuczynski$^{73}$, 
Kevin Tritz$^{74}$, 
Martin Thoma$^{75}$, 

@@

$^{39}$Department of Clinical Sciences Lund, Lund University, Lund, Sweden, 
$^{40}$HQ, Orexplore, Torshamnsgatan 30B, Stockholm, Sweden, 
$^{41}$Statistics Department, University of California - Davis, Davis, CA 95616, USA, 
$^{42}$Emory University, Atlanta, GA 30322, USA, 
$^{43}$Applied BioMath, 561 Virginia Rd Ste 220, Concord, MA 01742, USA, 
$^{44}$Department of Computer Science, University of Oxford, Wolfson Building, Parks Road, OX1 3QD Oxford, UK, 
$^{45}$NeuroInformatics Laboratory, Bruno Kessler Foundation, Trento 38123, Italy, 
$^{46}$Department of Engineering, University of Cambridge, Trumpington St, Cambridge CB2 1PZ, UK, 
$^{47}$Aix Marseille Universit\'e., CNRS, Centrale Marseille, LMA, Marseille, France, 
$^{48}$Interdisciplinary Center for Scientific Computing (IWR), Heidelberg University, Im Neuenheimer Feld 205 69120 Heidelberg, Germany, 
$^{49}$ABB Corporate Research, ABB AG, Wallstadter Str. 59 68526 Ladenburg, Germany, 
$^{50}$Institut f\"ur Mathematische Optimierung, Technische Universit\"at Carolo-Wilhelmina zu Braunschweig, Universit\"atsplatz 2 38106 Braunschweig, Germany, 
$^{51}$Independent Researcher, Cologne, Germany, 
$^{52}$Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA, 
$^{53}$Institut f{\"u}r Physik, Universit{\"a}t Augsburg, Universit{\"a}tsstra{\ss}e 1, 86135 Augsburg, Germany, 
$^{54}$Applied Research Laboratories, The University of Texas at Austin, P.O. Box 8029 Austin, TX 78713, USA, 
$^{55}$Department of Radiology, School of Medicine, University of Cincinnati, Cincinnati, OH 45221, USA, 
$^{56}$Department of Radiology, Cincinnati Children's Hospital Medical Center, Cincinnati, OH 45229, USA, 
$^{57}$Ascent Robotics Inc., 1-6-10 Hiroo Shibuya Tokyo, Japan, 
$^{58}$ENSTA Bretagne, 2 rue François Verny, Brest, France, 
$^{59}$Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 1, 81679 M\"unchen, Germany, 
$^{60}$Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany, 
$^{61}$Independent Researcher, USA, 
$^{62}$Data Sciences, Chan Zuckerberg Biohub, San Francisco, CA 94158, USA, 
$^{63}$Faculty of Mechanical Engineering, University of Ljubljana, A\v{s}ker\v{c}eva 6 1000 Ljubljana, Slovenia-EU, 
$^{64}$Sydney Informatics Hub, The University of Sydney, NSW 2006, Australia, 
$^{65}$Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'{o}lica de Chile, Casilla 306, Santiago 22, Chile, 
$^{66}$Max Planck Institute for Extraterrestrial Physics, Giessenbachstrasse, 85741 Garching, Germany, 
$^{67}$University of Stuttgart, Machine Learning and Robotics Lab, Universitätsstr. 38, 70569 Stuttgart, Germany, 
$^{68}$Department of Electrical Engineering, Universidade Federal de Campina Grande, 58429900 PB, Brazil, 
$^{69}$Department of Computer Science, Kiel University, 24098 Kiel, Germany, 
$^{70}$Planetary Sciences Group and Florida Space Institute and Department of Physics, University of Central Florida, 4111 Libra Drive Orlando Florida 32816-2385, USA, 
$^{71}$Independent Researcher, Spain, 
$^{72}$Monash Micro Imaging, Monash University, Clayton VIC 3800, Australia, 
$^{73}$Department of Molecular, Cellular, and Developmental Biology, University of Colorado, Boulder, Boulder, CO 80303, USA, 
$^{74}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N. Charles Street, Baltimore, MD 21218, USA, 
$^{75}$Independent Researcher, Munich, Germany, 

>>>>

Christian H\"aggstr\"om$^{39}$, 
Clark Fitzgerald$^{40}$, 
David A. Nicholson$^{41}$, 
David R Hagen$^{42}$, 
Dmitrii V. Pasechnik$^{43}$, 
Emanuele Olivetti$^{44}$, 

@@

Eric Wieser$^{45}$, 
Fabrice Silva$^{46}$, 
Felix Lenders$^{47,48,49}$, 
Florian Wilhelm$^{50}$, 

@@

Gavin A. Price$^{51}$, 
Gert-Ludwig Ingold$^{52}$, 
Gregory E. Allen$^{53}$, 
Gregory R. Lee$^{54,55}$, 
Herv\'e Audren$^{56}$, 
Irvin Probst$^{57}$, 
J\"org P. Dietrich$^{58,59}$, 
Jacob Silterra$^{60}$, 
James T Webber$^{61}$, 
Janko Slavi\v{c}$^{62}$, 
Joel Nothman$^{63}$, 
Johannes Buchner$^{64,65}$, 
Johannes Kulick$^{66}$, 

@@

Jos\'e Vin\'icius de Miranda Cardoso$^{67}$, 
Joscha Reimer$^{68}$, 
Joseph Harrington$^{69}$, 
Juan Luis Cano Rodr\'iguez$^{70}$, 
Juan Nunez-Iglesias$^{71}$, 
Justin Kuczynski$^{72}$, 
Kevin Tritz$^{73}$, 
Martin Thoma$^{74}$, 
Matthew Newville$^{75}$, 

@@

$^{39}$HQ, Orexplore, Torshamnsgatan 30B, Stockholm, Sweden, 
$^{40}$Statistics Department, University of California - Davis, Davis, CA 95616, USA, 
$^{41}$Emory University, Atlanta, GA 30322, USA, 
$^{42}$Applied BioMath, 561 Virginia Rd Ste 220, Concord, MA 01742, USA, 
$^{43}$Department of Computer Science, University of Oxford, Wolfson Building, Parks Road, OX1 3QD Oxford, UK, 
$^{44}$NeuroInformatics Laboratory, Bruno Kessler Foundation, Trento 38123, Italy, 
$^{45}$Department of Engineering, University of Cambridge, Trumpington St, Cambridge CB2 1PZ, UK, 
$^{46}$Aix Marseille Universit\'e., CNRS, Centrale Marseille, LMA, Marseille, France, 
$^{47}$Interdisciplinary Center for Scientific Computing (IWR), Heidelberg University, Im Neuenheimer Feld 205 69120 Heidelberg, Germany, 
$^{48}$ABB Corporate Research, ABB AG, Wallstadter Str. 59 68526 Ladenburg, Germany, 
$^{49}$Institut f\"ur Mathematische Optimierung, Technische Universit\"at Carolo-Wilhelmina zu Braunschweig, Universit\"atsplatz 2 38106 Braunschweig, Germany, 
$^{50}$Independent Researcher, Cologne, Germany, 
$^{51}$Lawrence Berkeley National Laboratory, Berkeley, CA 94720, USA, 
$^{52}$Institut f{\"u}r Physik, Universit{\"a}t Augsburg, Universit{\"a}tsstra{\ss}e 1, 86135 Augsburg, Germany, 
$^{53}$Applied Research Laboratories, The University of Texas at Austin, P.O. Box 8029 Austin, TX 78713, USA, 
$^{54}$Department of Radiology, School of Medicine, University of Cincinnati, Cincinnati, OH 45221, USA, 
$^{55}$Department of Radiology, Cincinnati Children's Hospital Medical Center, Cincinnati, OH 45229, USA, 
$^{56}$Ascent Robotics Inc., 1-6-10 Hiroo Shibuya Tokyo, Japan, 
$^{57}$ENSTA Bretagne, 2 rue François Verny, Brest, France, 
$^{58}$Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 1, 81679 M\"unchen, Germany, 
$^{59}$Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany, 
$^{60}$Independent Researcher, USA, 
$^{61}$Data Sciences, Chan Zuckerberg Biohub, San Francisco, CA 94158, USA, 
$^{62}$Faculty of Mechanical Engineering, University of Ljubljana, A\v{s}ker\v{c}eva 6 1000 Ljubljana, Slovenia-EU, 
$^{63}$Sydney Informatics Hub, The University of Sydney, NSW 2006, Australia, 
$^{64}$Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'{o}lica de Chile, Casilla 306, Santiago 22, Chile, 
$^{65}$Max Planck Institute for Extraterrestrial Physics, Giessenbachstrasse, 85741 Garching, Germany, 
$^{66}$University of Stuttgart, Machine Learning and Robotics Lab, Universitätsstr. 38, 70569 Stuttgart, Germany, 
$^{67}$Department of Electrical Engineering, Universidade Federal de Campina Grande, 58429900 PB, Brazil, 
$^{68}$Department of Computer Science, Kiel University, 24098 Kiel, Germany, 
$^{69}$Planetary Sciences Group and Florida Space Institute and Department of Physics, University of Central Florida, 4111 Libra Drive Orlando Florida 32816-2385, USA, 
$^{70}$Independent Researcher, Spain, 
$^{71}$Monash Micro Imaging, Monash University, Clayton VIC 3800, Australia, 
$^{72}$Department of Molecular, Cellular, and Developmental Biology, University of Colorado, Boulder, Boulder, CO 80303, USA, 
$^{73}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N. Charles Street, Baltimore, MD 21218, USA, 
$^{74}$Independent Researcher, Munich, Germany, 
$^{75}$Center for Advanced Radiation Sources, The University of Chicago, Chicago, IL 60637, USA, 
